---
title: "Global Warming Data Collection and Display"
author: "Zach Wilson"
date: "December 12, 2016"
output: beamer_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

```{r, echo = FALSE, include = FALSE} 
# load libraries
library(tidyverse)
```

```{r, echo = FALSE, include = FALSE} 
# load all data for presentation
source("data_load_and_clean.R")
```

## Introduction
- Recent election results have brought a group of people into the lime light who the media refers to as climate change deniers
- This groups prominence in recent news cycles prompted me to take a look at some of the key data sets currently being used to demonstate that global warming is a real and is likely attributable to human actions

## What is the Green House Effect
- Energy from the sun drives the Earth's climate and heats the Earth's Surface
- The Earth radiates some of this energy back into space
- Some atmospheric gases trap some of this radiated energy and retain it
- These gases are known as green house gasses
- The greenhouse effect is the rise in tempeature of the Earth as as these green house gasses in the atmosphere trap energy

- There are six main green house gasses - carbon dioxide, methane, nitrous oxide, hydrofluorocarbons, perfluorocarbons, and sulphur hexafluoride

## Why Is This A Bad Thing?
```{r co2}
ggplot(co2_old, aes(-1*age, co2_ppm)) + geom_point() + geom_line() +
           geom_point(data = co2_recent, aes(decimal_date - 1958.208, interpolated)) + geom_line() +
           ggtitle("Ice Core CO_2 Data") +
           labs(x = "Year", y = "CO_2 (parts per million)")
```

## Mauna Loa $CO_2$ Data
```{r ml}
ggplot(co2_recent, aes(decimal_date, interpolated)) + geom_point() + geom_line() + 
           ggtitle("Monthly Mean CO_2 at Mauna Loa") +
           labs(x = "Year", y = "CO_2 (parts per million)")
```

## Data For the Project
Data from multiple sources was gathered, it ranged from clean and ready for use to quite dirty and in multiple different files that had to be downloaded, merged, and cleaned.

- National Oceanic and Atmospheric Admisistration
- Snow and Ice Data Center
- Environmental Protection Agency
- National Climatic Data Center
- United Kingdom Meterology Office

## Shiny App Demo

## Backup

## Backup
- Unfortunately the human race drives the production of large amounts of green house gasses
- Green house gases are actually one of the reasons this planet is habitable